Accurate Description of Cation Binding to Lipid Bilayers with Negatively Charged Phosphatidylserine Requires Accounting for Electronic Polarization

### 2019-07-11 Manuscript/manuscript.tex

\title[] 
{Improved Description of Cation Binding to Lipid Bilayer with Negatively Charged POPS by Effective Inclusion of Electronic Polarization}
  %Detailed structure of negatively charged membranes 
  %  of phosphatidylserine and phosphatidylcholine 
  %  at concentrations of calcium, sodium and potassium salts
  %  from molecular dynamics simulations with electronic polarization }
  % JOSEF: I feel that the above title is a bit better, because it focuses on PS,
  %        but the following one is an alternative, which focuses more on the cations as in roux90
  %{ Detailed structure of calcium, sodium and potassium cations
  %  at negatively charged membranes of phosphatidylserine and phosphatidylcholine 
  %  from molecular dynamics simulations with electronic polarization }

@@

Phosphatidylserine (PS) lipids are the most common negatively charged lipids in eukaryotic membranes
and important signaling molecules \cite{lemmon08,leventis10,li14}.
They interact with signaling proteins \cite{leventis10},
regulate surface charge and protein localization \cite{yeung08}, 
induce protein aggregation \cite{zhao04,gorbenko06} and membrane fusion \cite{??}.
As these functions are also often regulated by ions \cite{leventis10},
a detailed understanding of interactions between negatively charged lipids and biologically relevant cations such as calcium is of a great importance.
As a recent example, we have shown by a combination of spectroscopic experiments, biochemical essays, and molecular simulations, that binding of
calcium to PIP2 lipids inhibits their recognition by a phospolipase C, which demonstrates that not only proteins but also lipids can get involved in calcium 
signaling \cite{DOI: 10.1021/jacs.6b11760}.

>>>>

\title[] 
{Accurate Description of 
Cation Binding to Lipid Bilayers 
with Negatively Charged Phosphatidylserine 
Requires Accounting for Electronic Polarization}
  %Detailed structure of negatively charged membranes 
  %  of phosphatidylserine and phosphatidylcholine 
  %  at concentrations of calcium, sodium and potassium salts
  %  from molecular dynamics simulations with electronic polarization }
  % JOSEF: I feel that the above title is a bit better, because it focuses on PS,
  %        but the following one is an alternative, which focuses more on the cations as in roux90
  %{ Detailed structure of calcium, sodium and potassium cations
  %  at negatively charged membranes of phosphatidylserine and phosphatidylcholine 
  %  from molecular dynamics simulations with electronic polarization }

@@

Phosphatidylserine (PS) lipids are the most common negatively charged lipids in eukaryotic membranes
and important signaling molecules \cite{lemmon08,leventis10,li14}.
They interact with signaling proteins \cite{leventis10},
regulate surface charge and protein localization \cite{yeung08}, 
induce protein aggregation \cite{zhao04,gorbenko06} and membrane fusion \cite{wilschut1981calcium, papahadjopoulos90, verma2018cell}.
As these functions are also often regulated by ions \cite{leventis10},
a detailed understanding of interactions between negatively charged lipids and biologically relevant cations such as calcium is of a great importance.
As a recent example, we have shown by a combination of spectroscopic experiments, biochemical essays, and molecular simulations, that binding of
calcium to \ce{PIP_2} lipids inhibits their recognition by a phospolipase C, which demonstrates that not only proteins but also lipids can get involved in calcium 
signaling \cite{Bilkova2017Calcium}.
